Quality assurance of digital twins -- An experience report in the automotive industry

### 2023-03-02 manuscripts/paper-1/main.tex
Results and discussion is partly done

\documentclass{llncs}
\usepackage[colorlinks,allcolors=blue]{hyperref}
\usepackage[T1]{fontenc}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{verbatim}
\usepackage{cite}

@@

    \textbf{Fidelity}
    Fidelity refers to the degree of exactness with which the real system is copied and represented. Low fidelity indicates a simplified representation, 
    while high-fidelity refers to an accurate and detailed representation of the real system \cite{Review2}. 
    The concept of fidelity has garnered significant attention in recent years and continues to be an important area of research in digital twins\cite{Review2}\cite{Review1}.

    \textbf{Efficiency}
    Efficiency refers to the quality of being efficient, and efficiency is achieving
    maximum productivity with minimum wasted effort or expense. The concept of efficiency is tightly coupled to productivity, which refers to the quality of being productive,
    also the word productive can be explained as producing or being able to produce large amounts of goods\cite{OxfordDictionary}.  
    For example, time efficiency indicates that,  with less amount of time as an input, more output with the minimum 
    waste during the process is desired. Goods of the digital twin are nothing but information, which Grieves first 
    indicated with this Information Mirror Model\cite{GrievesPLMBook}.

    \textbf{Evolvability}
    A system's capability to enhance its suitability to its environment through alterations to both its internal and functional 
    structure is referred to as evolvability\cite{MobusSystemTheory}. Another term used to describe the response to changes in the environment is adaptability.
    However, this concept differs from evolvability in that it only affects a system's internal or functional structure temporarily. 
    For instance, a digital twin, which is a virtual system, can be designed to be more flexible and scalable, 
    allowing for easy updates and the addition of new features. 
    These updates and new features will result in definite changes to the structure of the system. 
    On the other hand, a responsive web design is an adaptable system, capable of adjusting its size and layout 
    depending on the user's hardware. As we have seen in \cite{ZHANGUPDATEMETHOD}, the update method shows that digital twins are evolvable systems, 
    hence this attribute should be considered when the digital twin's quality is inspected. To assess the evolvability attribute, scalability analysis,
    reusability analysis, modifiability analysis, testability analysis, and maintainability analysis can be performed. 
    \section{Artifacts and Methods}
    The used methodology consists of manual artifact reviews and evaluation of the results according to the digital twin quality attributes.    
    \subsection{Artifacts}
    The current stage of review encompasses five key artifacts, including process videos displaying the current assembly procedure without an adaptive workstation and cobot, a scope definition outlining the objects on the shop floor requiring tracking or twinning, a requirements specification summarizing functional and non-functional requirements for the digital twin, a general and an operational conceptual model elucidating the high-level structure of the assembly procedure, 
    and a discrete event simulation module that implements the structures prescribed by the conceptual models.

@@

    \section{Results}

@@

    \subsection{Manual Review Result}
    \subsection{Quality Inspection with Quality Attributes}
    As can be seen in Figures and ~\ref{fig:QualityInspectonResultsWithArtifacts}, based on our inspection of the given artifacts,
    we have identified a total of seven correctness issues, eleven completeness issues, and two fidelity issues. 
    It is important to note that we were unable to inspect for efficiency as the project is still in the design phase, 
    and we do not have enough data to make estimations for this attribute. Additionally, all of our inspections were conducted manually, 
    which is susceptible to human error and inspector bias.
    \section{Discussion}
    \label{section:framework_1}
    To mitigate potential human bias and enhance the data-driven approach for quality assurance, ongoing research aims to address these issues. 
    Furthermore, the assessment of digital twin quality can be significantly improved by obtaining data from real systems, thereby enabling better visibility and a more robust evaluation. As such, the use of empirical data in combination with machine learning techniques can offer a more objective and reliable means of evaluating the correctness, completeness, fidelity, efficiency, and evolvability of digital twins. Additionally, given the manual nature of the current inspections, it is important to acknowledge the potential for inspector bias, which may impact the accuracy of the assessments. 
    By leveraging technology to automate certain aspects of the evaluation process, it is possible to reduce the potential for such biases and improve the overall quality of digital twin assessments.

>>>>

\documentclass{llncs}
\usepackage[colorlinks,allcolors=blue]{hyperref}
\usepackage[T1]{fontenc}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{verbatim}
\usepackage{cite}
\usepackage{booktabs}
\usepackage{multirow}

@@

    \textbf{Fidelity} refers to the degree of exactness with which the real system is copied and represented. Low fidelity indicates a simplified representation, 
    while high-fidelity refers to an accurate and detailed representation of the real system \cite{Review2}. 
    The concept of fidelity has garnered significant attention in recent years and continues to be an important area of research in digital twins\cite{Review2}\cite{Review1}.

    \textbf{Efficiency} refers to the quality of being efficient, and efficiency is achieving
    maximum productivity with minimum wasted effort or expense. The concept of efficiency is tightly coupled to productivity, which refers to the quality of being productive,
    also the word productive can be explained as producing or being able to produce large amounts of goods\cite{OxfordDictionary}.  
    For example, time efficiency indicates that,  with less amount of time as an input, more output with the minimum 
    waste during the process is desired. Goods of the digital twin are nothing but information, which Grieves first 
    indicated with this Information Mirror Model\cite{GrievesPLMBook}.

    \textbf{Evolvability} is a system's capability to enhance its suitability to its environment through alterations to both its internal and functional 
    structure\cite{MobusSystemTheory}. Another term to describe the response to changes in the environment is adaptability.
    However, this concept differs from evolvability in that it only affects a system's internal or functional structure temporarily. 
    For instance, a digital twin, which is a virtual system, can be designed to be more flexible and scalable, 
    allowing for easy updates and the addition of new features. 
    These updates and new features will result in definite changes to the structure of the system. 
    On the other hand, a responsive web design is an adaptable system, capable of adjusting its size and layout 
    depending on the user's hardware. As we have seen in \cite{ZHANGUPDATEMETHOD}, the update method shows that digital twins are evolvable systems, 
    hence this attribute should be considered when the digital twin's quality is inspected. To assess the evolvability attribute, scalability analysis,
    reusability analysis, modifiability analysis, testability analysis, and maintainability analysis can be performed. 
    \section{Artifacts and Methods}
    The used methodology consists of manual artifact reviews and evaluation of the results according to the digital twin quality attributes.    
    \subsection{Artifacts}
    The current stage of review encompasses five key artifacts, including process videos displaying the current assembly procedure without an adaptive workstation and cobot, a scope definition outlining the objects on the shop floor requiring tracking or twinning, a requirements specification summarizing functional and non-functional requirements for the digital twin, a general and an operational conceptual model elucidating the high-level structure of the assembly procedure, 
    and a discrete event simulation module that implements the structures prescribed by the conceptual models.

@@

    \section{Results}
    During the initial stages of the project, when the target system was not yet available, there was a 
    lack of observable data about system behavior that could be utilized for validation. Instead, informal and potentially incomplete, inconsistent, or incorrect system descriptions had to be relied upon. 
    Therefore, manual reviews for each artifact were conducted and twenty-one issues were identified and mapped to the specific digital twin quality attributes. 
    The analysis revealed that a total of thirty-eight digital twin quality attributes were lacking in these artifacts. \ref{fig:QualityInspectonResultsWithArtifacts}

\textbf{Process Videos Review Results}

F1  - Even though the videos are well suited for providing a first impression of the production facility and the current assembly process for one product variant, the other product variants include different assembly operations, 
which were not shown in the videos. Furthermore, the cobot and the adaptive workstation were not part of the assembly process yet, hence the videos do not provide a complete representation of the target system.

\textbf{Scope Definition Review Results}

F2 - The scope definition focuses on the physical entities of the shop floor and is consistent with the videos presented in the previous section. 
However, the scope definition is incomplete. Several entities are only selected for the tracking, hence additional state information such as the failure status of these entities was missing in the digital twin.

\textbf{Requirements Specification Review Results}

F3-  Atypical categorization of the digital twin requirements as functional, non-functional, constraint and standard was introduced. 
Also, standard categories were considered as a cause of requirements instead of a category of requirements. Furthermore, 
the constraint category was considered a non-functional requirement which results in a significant misunderstanding between non-functional 
requirements and constraints. Finally, some requirements were described as non-functional requirements instead of functional requirements.

F4 - Imprecise and unclear statements were found in requirement specifications.

F5 - Key design decisions were found in the requirement specifications, which results in a considerable decrease in maintainability.

\textbf{Conceptual  Model Review Results}

F6 - Conceptual models are not designed to react to unwanted situations.

F7 - Conceptual model specification was not clear enough, which results in quite some room for interpretations by the stakeholders. 
as the use of an unspecified flow chart model is prone to differing interpretations by different stakeholders and probable incorrect understanding of the relations between the sub-systems.

F8 - The difference between the event triggers and decision nodes was not clear, which decreased the clarity and maintainability of the model considerably.

F9 - Representation of the model is not great, hence understanding the interactions between the different subprocesses are not clear.

F10 - The model were lacking great organization tools such as swim lanes and object flows.

F11 - The assignment of the cobot to micro-operations was not regularly reviewed and updated as the project progresses.

F12 - Even though the durations of the macro-operations were well-known and studied thoroughly before, the durations of the micro-operations were estimated based on a simple calculation scheme.

\textbf{Simulation Model Review Results}

F13:The input controls in the Discrete  Event Simulation module were not complete or aligned with the actual inputs that will be provided by another system.

F14, F15:The ranges defined for some events were not validated.

F16:Database structures were not updated automatically, instead done manually.

F17:The duration of micro-, loading- and unloading-operations of the cobot were based on assumptions rather than actual measurements.

F18:Discerete Event Simulation module does not support parallel execution of micro-operations.

F19:Interruption mechanism of the assembly line was not considered within the DES module.

F20:Number of micro-operations were hard coded, consequently, the DES module must be reprogrammed every time, when a new micro-operation is needed.

F21:Edge-cases were not considered in the DES module.

@@

    \section{Discussion}
    \label{section:framework_1}
    To mitigate potential human bias and enhance the data-driven approach for quality assurance, ongoing research aims to address these issues. 
    Furthermore, the assessment of digital twin quality can be significantly improved by obtaining data from real systems, thereby enabling better visibility and a more robust evaluation. As such, the use of empirical data in combination with machine learning techniques can offer a more objective and reliable means of evaluating the correctness, completeness, fidelity, efficiency, and evolvability of digital twins. Additionally, given the manual nature of the current inspections, it is important to acknowledge the potential for inspector bias, which may impact the accuracy of the assessments. 
    By leveraging technology to automate certain aspects of the evaluation process, it is possible to reduce the potential for such biases and improve the overall quality of digital twin assessments.
